Optimizing Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD

### 2019-10-07 paper/cvpr2020/sections/hardware.tex
Updated teaser, moved supplement figures to gdrive.
Update paper, add z compensation for SPAD.

\begin{figure}[H]
  \includegraphics[width=\linewidth]{prototype_single_col.png}
  \caption{Prototype scanning setup. The pulsed light from the laser travels
    through a beam splitter before being guided by the galvo to the scene.
    Returning light is measured by the single-pixel SPAD. The RGB camera of a
    Kinect v2 is used to capture the monocular RGB image (the depth camera is
    not used)}
  \label{fig:prototype}
\end{figure}

@@

\textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}

>>>>

\begin{figure}[H]
  \includegraphics[width=\linewidth]{prototype_single_col.pdf}
  \caption{Prototype scanning setup. The pulsed light from the laser travels
    through a beam splitter before being guided by the galvo to the scene.
    Returning light is measured by the single-pixel SPAD. The RGB camera of a
    Kinect v2 is used to capture the monocular RGB image (the depth camera is
    not used)}
  \label{fig:prototype}
\end{figure}

@@

We determined camera intrinsics and extrinsics for the Kinect's RGB camera and
the scanning system using the standard camera calibration toolbox in MATLAB.
In general it is impossible to compensate for the offset between camera and
SPAD, but we do add the z displacement from spad to kinect to partially
compensate for it.
% \textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}

### 2019-10-07 paper/cvpr2020/sections/related.tex
Update paper, add z compensation for SPAD.

\textcolor{red}{Our method is essentially a modified form of the algorithm in \cite{Morovic2002}, modified for our particular use case. Also worth noting is the fact that most algorithms compute histograms from existing images, whereas our method mesaures the depth histogram indirectly using photon arrivals.} Note: this paragraph needs more work. We can say something like ``Inspired by Morovic et al., we do something'' but then we also need to highlight how our method is different. Perhaps concisely summarize how you adapt it for our SPAD model.
%
% \begin{itemize}
%   \item Exact histogram matching paper used in this work
%   \item Wasserstein-based optimization techniques for
%     histogram-based regularization
% \end{itemize}

>>>>

Because the single SPAD produces a weighted histogram of the depth map, we adapt
the algorithm in Morovic et al. to accommodate general per-pixel
weights, which allows us to compensate for different scene reflectances during
the histogram matching.
% \textcolor{red}{Our method is essentially a modified form of the algorithm in \cite{Morovic2002}, modified for our particular use case. Also worth noting is the fact that most algorithms compute histograms from existing images, whereas our method mesaures the depth histogram indirectly using photon arrivals.} Note: this paragraph needs more work. We can say something like ``Inspired by Morovic et al., we do something'' but then we also need to highlight how our method is different. Perhaps concisely summarize how you adapt it for our SPAD model.
%
% \begin{itemize}
%   \item Exact histogram matching paper used in this work
%   \item Wasserstein-based optimization techniques for
%     histogram-based regularization
% \end{itemize}
